Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{{DISTRIBUTION STATEMENT A. Approved for public release.} }

### 2021-05-14 paper/intro.tex
Updates from Overleaf

All the aforementioned tools are publicly available \cite{fmide}, as is the motivating example \cite{repo}, and the full UxAS model with its deployment in seL4, demonstration videos, etc. \cite{phase2, camkes} ---ADD LINK TO VIDEO.

>>>>

The BriefCASE tools are open source and publicly available \cite{fmide}, as is the motivating example \cite{repo}, and the full UxAS model with its deployment in seL4 \cite{phase2, camkes}.  Videos demonstrating the use of the BriefCASE tools to build the UAV example presented in Section~\ref{sec:case-study} are available at \mbox{loonwerks.com/projects/case}.
